Postural changes mediate children's visual access to social information

### 2018-01-15 writeup-cogsci-copy/cogsci2018.Rmd
>1 keypioint

data_openpose_hands <- read_csv("../data/final_output/openpose_results_with_detail_hands.csv") %>%
  distinct(name, frame, .keep_all = TRUE) %>%
  mutate(video = name) %>%
  distinct(video,frame,.keep_all=TRUE)  %>%
  select(group, video,frame,ends_with("conf")) %>%
  mutate(confLeft=rowSums(.[grep("hand_left", names(.))])/21)  %>%
  mutate(confRight=rowSums(.[grep("hand_right", names(.))])/21)  %>%
  mutate(is_hand = ifelse(confRight>=.5 | confLeft>=.5, "True", "False"))

>>>>

data_openpose_hands <- read_csv("../data/final_output/openpose_results_with_detail_hands.csv") %>%
  distinct(name, frame, .keep_all = TRUE) %>%
  mutate(video = name) %>%
  distinct(video,frame,.keep_all=TRUE)  %>%
  select(group, video,frame,ends_with("conf")) %>%
  mutate(confLeft=rowSums(.[grep("hand_left", names(.))])/21)  %>%
  mutate(confRight=rowSums(.[grep("hand_right", names(.))])/21)  %>%
  mutate(is_hand = ifelse(confRight>=.05 | confLeft>=.05, "True", "False"))
